Contextuality and Nonlocality in \\ Discrete Quantum Theory

### 2015-11-21 DQC3.tex
Re: Yu-Tsung Tai wants to share "Erratum: Geometry of discrete...
From: JOHN GOLDEN GARDINER [mailto:johngardiner@ucla.edu] 
Sent: Friday, November 20, 2015 22:51
To: Tai, Yu-Tsung <yuttai@indiana.edu>
Subject: Re: Yu-Tsung Tai wants to share "Erratum: Geometry of discrete
quantum computing" with you

I think

Department of Physics and Astronomy, University of California, Los
Angeles, CA 90095, USA

would be better to use.

Thanks,
John

On Fri, Nov 20, 2015 at 6:49 PM, Tai, Yu-Tsung <yuttai@indiana.edu>
wrote:
Dear all, 
 
I changed it to “unentangled states,” and I am about to submit our
Err

\address{$^{1}$ College of Physical and Mathematical Sciences, Brigham Young
University, Provo, UT 84602, U.S.A}

\address{$^{2}$ School of Informatics and Computing, Indiana University,
Bloomington, IN 47405, U.S.A}

\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
47405, U.S.A}

\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, U.S.A}

>>>>

\address{$^{1}$ Department of Physics and Astronomy, University of California,
Los Angeles, CA 90095, USA}

\address{$^{2}$ School of Informatics and Computing, Indiana University,
Bloomington, IN 47405, USA}

\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
47405, USA}

\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, USA}
